---
title: "Fed-Prov Realtime Hydrometric Network Lag"
author: "hydrolook package"
date: "Generated on: `r Sys.Date()` "
output:
  pdf_document:
    toc: true
    fig_caption: yes
  html_document:
    toc: true
    fig_caption: yes
params:
  table_format:
    value: latex
  prov:
    value: PE
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# Copyright 2017 Province of British Columbia
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and limitations under the License.

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 8, fig.path = "./")



library(tidyhydat)
library(hydrolook)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(knitr)
library(kableExtra)

options(knitr.table.format = params$table_format) 

```


```{r, message=FALSE, warning=FALSE, echo = FALSE}
prov <- params$prov
bc_lag <- check_realtime_lag(PROV_TERR_STATE_LOC = prov)
#bc_lag <- check_realtime_lag(STATION_NUMBER = c("08NL071","08LG048"))

#bc_lag
```

# Summary
Summary of difference between most recent observation and uploaded time
```{r, echo = FALSE}
lag_tbl <- bc_lag %>%
  filter(!is.na(time_lag_num)) %>%
  summarise_at(vars(time_lag_num), funs(mean, median, sd, min, max, n()))

cat(paste0("Province surveyed: ", prov))

if (params$table_format == "latex"){
kable(lag_tbl, format = "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "HOLD_position")) %>%
  #kable_styling(bootstrap_options = c("striped", "hover"))  %>%
  add_footnote(c("Values presented in hours"), notation = "number")
}

if (params$table_format == "html"){
  kable(lag_tbl, format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))  %>%
  add_footnote(c("Values presented in hours"), notation = "number")
}

```

```{r}
#existing_data = read_csv("C:/_dev/Git_repos/hydrolook_output/report/Realtime_lag/lag_record.csv")
#
#lag_tbl %>%
#  mutate(Datetime = Sys.time()) %>%
#  bind_rows(existing_data) %>%
#  write_csv("C:/_dev/Git_repos/hydrolook_output/report/Realtime_lag/lag_record.csv") %>%
#  gather(vars, value, -Datetime, -n) %>%
#  ggplot(aes(x = Datetime, y = value, colour = vars)) +
#  geom_point() +
#  scale_x_datetime(date_labels = "%b %d") +
#  geom_line()
```


# Distribution of Data Lag
```{r, warning=FALSE, fig.height = 6}
num_stations = nrow(bc_lag)

bc_lag %>%
  mutate(Grouping = case_when(
   time_lag_num >= 1000 ~ "Over 1000 minutes", 
   time_lag_num < 1000 ~ "Under 1000 minutes"
  )  ) %>%
  filter(!is.na(Grouping)) %>%
  ggplot(aes(x = time_lag_num)) +
  geom_histogram() +
  geom_rug() +
  labs(x = "Difference between upload time and most recent observations (minutes)",
       y = "Number of Ocurrences",
       title = paste0("Realtime Hydrometric Station Data Lag (n = ",num_stations,")"),
       subtitle = "Each station was pinged for the most recent hydrometric observation. The difference between this value and the time of data upload is considered the lag time" ) +
  facet_wrap(~Grouping, scales = "free_x") +
  theme_minimal()
```

# Stations greater than 10 hour lag
```{r}
big_lags <- bc_lag %>%
  filter(time_lag_num > 10) %>%
  left_join(bcstations, by = c("STATION_NUMBER")) %>%
  select(STATION_NUMBER, STATION_NAME, time_obs, time_mod, time_lag) %>%
  arrange(time_lag)

if (nrow(big_lags) == 0){
  cat("No stations with a lag greater than 10 hours")
}

if (params$table_format == "latex" && nrow(big_lags) > 0){
  kable(big_lags, format = "latex", longtable = T, booktabs = T) %>%
    kable_styling(font_size = 8, latex_options = c("striped","HOLD_position","repeat_header")) %>%
    add_footnote(c("Values presented in hours"), notation = "number")
}

if (params$table_format == "html" && nrow(big_lags) > 0){
  kable(big_lags, format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))  %>%
    add_footnote(c("Values presented in hours"), notation = "number")
}
```

# Stations that have not being updated in the last 24 hours
```{r}
cat("Current date and time:")
print(Sys.time())

not_updating <- bc_lag %>%
  filter(time_obs < Sys.time() - (24*60*60)) %>%
  left_join(bcstations, by = c("STATION_NUMBER")) %>%
  select(STATION_NUMBER, STATION_NAME, time_obs) %>%
  arrange(time_lag)

if (nrow(not_updating) == 0){
  cat("All stations have updated measurements taken within the last 24 hours")
}

if (params$table_format == "latex" && nrow(big_lags) > 0){
  kable(not_updating, format = "latex", longtable = T, booktabs = T) %>%
    kable_styling(font_size = 8, latex_options = c("striped","HOLD_position","repeat_header")) 
}

if (params$table_format == "html" && nrow(big_lags) > 0){
  kable(not_updating, format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover")) 
}
```

# License

    Copyright 2017 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
