---
output:
  pdf_document:
    fig_caption: yes
  html_document:
    toc: true
    fig_caption: yes
params:
  region:
    value: "West Coast Natural Resource Region"
  date:
    value: !r Sys.Date()
  table_format:
    value: latex
geometry: margin=2cm
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

---
title: "`r params$region`"
---

```{r packages, include=FALSE}
library(tidyverse)
library(bcmaps)
library(tidyhydat)
library(lubridate)
library(sf)
library(rmapshaper)
library(kableExtra)
library(knitr)
library(RcppRoll)
library(ggrepel)
```
 
```{r setup, include=FALSE}

## Knitr options dependent on type of document
if(params$table_format == "latex"){
  opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8, fig.height = 8, fig.path = file.path("report/regional_streamflow/"))
}

if(params$table_format == "html"){
  opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8, fig.height = 8)
}

options(knitr.table.format = params$table_format)
#params <- tibble(region = "Skeena Natural Resource Region")
```


```{r functions}
## Calculate percentiles from tidyhydat extracted data
## Limited to current day calculation
calc_percentiles <- function(historical_flow, realtime_data) {
  
  if(class(realtime_data$Date) != "Date") stop("Date column is not in date class")
  
  historical_flow %>%
    filter(yday(Date) == yday(Sys.Date())) %>%
    group_by(STATION_NUMBER) %>%
    nest() %>%
    left_join(realtime_data, by = c("STATION_NUMBER")) %>%
    mutate(prctile = map2_dbl(data, Value, ~ecdf(.x$Value)(.y))) %>%
    left_join(allstations, by = c("STATION_NUMBER")) %>%
    mutate(pct_bin = case_when(
      is.na(prctile) ~ "Not ranked",
      prctile >= 0 & prctile <= 0.01 ~ "Low",
      prctile > 0.01 & prctile <= 0.10 ~ "Much below normal (<10)",
      prctile > 0.10 & prctile <= 0.24 ~ "Below Normal (10-24)",
      prctile > 0.24 & prctile <= 0.75 ~ "Normal (25-75)",
      prctile > 0.75 & prctile <= 0.90 ~ "Above normal (76-90)",
      prctile > 0.90 & prctile < 1 ~ "Much above normal (>90)",
      prctile == 1 ~ "High"
    )) %>%
    mutate(pct_bin = factor(pct_bin, levels = expected)) %>%
    mutate(prctile = prctile*100) %>%
    st_as_sf(coords = c("LONGITUDE", "LATITUDE"),
             crs= 4326,
             agr= "constant") %>%
    transform_bc_albers()
}
```


```{r load}
## For testing
#params <- tibble(date = Sys.Date(),region = "West Coast Natural Resource Region")

## Load realtime stations and convert to spatial object
stns_sf <-  st_as_sf(
    realtime_stations(prov_terr_state_loc = "BC"),
    coords = c("LONGITUDE", "LATITUDE"),
    crs = 4326,
    agr = "constant"
  ) %>%
  transform_bc_albers()
```


```{r clean}
### Spatial Cleaning

## Choose the correct region
nr_regions_sub <- filter(nr_regions(), ORG_UNIT_NAME == params$region) 


## Find the inters
region_borders <- st_intersection(nr_regions_sub, bc_bound_hres()) 

region_rivers <- st_intersection(nr_regions_sub, watercourses_5M())

wsc_drainages <- ms_simplify(wsc_drainages())

region_watershed <- st_intersection(select(nr_regions_sub, SHAPE), wsc_drainages()) %>%
  group_by(SUB_DRAINAGE_AREA_NAME) %>%
  summarise() %>%
  ms_simplify()

stns_region <- st_join(stns_sf, nr_regions_sub, left = FALSE) 

city <- bc_cities() %>%
  st_join(region_borders, left = FALSE) %>%
  filter(POP_2000 == max(POP_2000)) %>%
  rename(geometry = SHAPE) %>%
  mutate(
    CENTROID = map(geometry, st_centroid),
    COORDS = map(CENTROID, st_coordinates),
    COORDS_X = map_dbl(COORDS, 1),
    COORDS_Y = map_dbl(COORDS, 2)
  ) %>%
  as_tibble() %>%
  st_sf() 

```

```{r analysis_instant}
## All stations from the specified region, that are flow and 
## have a record longer than 20 years
q_stns <- unique(stns_region$STATION_NUMBER) %>%
  hy_stn_data_range() %>%
  filter(DATA_TYPE == "Q") %>%
  filter(RECORD_LENGTH >=20) %>%
  pull(STATION_NUMBER)

## Query realtime data
rl_data <- realtime_dd(q_stns)

## Find most recent instantaneous discharge value
rl_data_instant <- rl_data %>%
  filter(Parameter == "Flow") %>%
  group_by(STATION_NUMBER) %>%
  filter(Date == max(Date)) %>%
  select(STATION_NUMBER, Date, Value) %>%
  mutate(Date = as.Date(Date)) %>%
  filter(Date == Sys.Date()) %>% ## drop max values that aren't today
  ungroup()

## Queery historical data
## NOTE: Should this be done with rl_data_recent$STATION_NUMBER?
hist_flow <- hy_daily_flows(q_stns)
```

This report was generated on
```{r, results='asis'}
cat(format(Sys.Date(), '%d %B, %Y'))
```

## Percentiles of Historical Flow

The information is taken from real time data recorded at WSC stations and is based on percentiles of long term  historical flows for that day. A percentile is a value on a scale of one hundred that indicates the percent of a distribution that is equal to or below it. In general:

- A streamflow which is greater than the 75th percentile is considered above normal
- A streamflow which is between 25th and 75th percentiles is considered normal
- A streamflow which is less than the 25 percentile is considered below normal
- A  Streamflow which is  less than 10 percentile is considered much below normal
- The flow category "Low" indicates that the estimated streamflow is the lowest value ever measured for the day of the year

Below are the maps with percentile data for WSC stations:

```{r 24h}
## Find the average of the last 24 hours
rl_data_last24 <- rl_data %>%
  filter(Parameter == "Flow") %>%
  group_by(STATION_NUMBER) %>%
  filter(Date >= Sys.time() - 60*60*24) %>% ## all data from last 24 hours
  select(STATION_NUMBER, Date, Value) %>%
  mutate(Date = Sys.Date()) %>% ## label last twenty four hours as from today
  group_by(Date, STATION_NUMBER) %>%
  summarise(Value = mean(Value)) %>%
  ungroup()
```


```{r 7day}
## Realtime 7 day average
## I took the realtime daily averages
rl_data_7day_mean <- rl_data %>%
  filter(Parameter == "Flow") %>%
  mutate(Date = as.Date(Date)) %>%
  group_by(Date, STATION_NUMBER) %>%
  summarise(Value = mean(Value, na.rm = TRUE)) %>%
  mutate(Value = roll_mean(Value, n = 7,na.rm = TRUE, fill = "right")) %>%
  #filter(Date == Sys.Date()) %>%
  ungroup()

hist_flow_7day_mean <- hist_flow %>%
  group_by(STATION_NUMBER) %>%
  mutate(Value = roll_mean(Value, n = 7, na.rm = TRUE, fill = "right")) %>%
  ungroup()
```


```{r calc_perc}
  ## Expected NAWW percentile bins
expected <- c("Not ranked", "Low","Much below normal (<10)", 
   "Below Normal (10-24)", "Normal (25-75)", 
   "Above normal (76-90)","Much above normal (>90)", "High")

## Calculate instantaneous percentiles 
pct_flow_instant <- calc_percentiles(hist_flow, rl_data_instant) 

## Calculate 24 hours percentiles
pct_flow_last24 <- calc_percentiles(hist_flow, rl_data_last24)

pct_flow_7day_mean <- calc_percentiles(hist_flow_7day_mean, rl_data_7day_mean)
```

```{r output, fig.height = 5.8, fig.width=6.4, fig.align="center"}

naww_pal <- c("#9c0ad1","#F90010","#B31F23","#FEA116","#08FA09","#46DED2","#0003F6","#000000")

## Create a named vector
named_naww_pal <- setNames(naww_pal, expected)


ggplot() +
  #geom_sf(data = region_borders, alpha = NA, fill = NA) +
  geom_sf(data = region_watershed, alpha = NA, fill = NA) +
  geom_sf(data = region_rivers, col = "blue") +
  geom_sf(data = pct_flow_instant, aes(colour = pct_bin, fill = pct_bin), size = 2) +
  #guides(colour = guide_legend(override.aes = list(size = 9, shape=15))) +
  geom_text_repel(city, mapping = aes(COORDS_X, COORDS_Y, label = NAME), 
                           size = 3, min.segment.length = 0) +
  geom_point(city, mapping = aes(COORDS_X, COORDS_Y), 
                           size = 3, shape = 17) +
  scale_colour_manual(name = "Streamflow Conditions", values = named_naww_pal, drop = FALSE) +
  scale_fill_manual(name = "Streamflow Conditions", values = named_naww_pal, drop = FALSE) +
  labs(x = NULL, y = NULL, 
       title = paste0(params$region),
       subtitle = paste0("Data represent instantaneous streamflow data from ", params$date, " compared to historical data")) +
  theme_minimal() + 
  coord_sf(datum = NA) +
  theme(plot.margin = margin(0,0,0,0))
```

### Percentile comparison
The following are comparisons of three percentile aggregations:

- %tile-instant is percentile of the most recent instantaneous discharge measurement from `r Sys.Date()` to the historical daily values
- %tile-last24 is percentile of the average of the last 24 hours of discharge measurements to the historical daily values
- %tile-7day_mean is percentile of the rolling 7 day average of daily mean discharge measurements to the 7 day rolling mean of the historical daily values. All 7 day means are calculated based on the **past 7 days**.

These are evaluated separately in this document.

```{r}
num_year_data <- hy_stn_data_range(unique(pct_flow_instant$STATION_NUMBER)) %>%
  filter(DATA_TYPE == "Q") %>%
  select(STATION_NUMBER, RECORD_LENGTH) %>%
  rename(`Record Length` = RECORD_LENGTH)

## Grab only the latest flow and merge into one data frame
pct_flow_instant_tbl_data <- pct_flow_instant %>%
  st_set_geometry(NULL) %>%
  select(STATION_NAME, STATION_NUMBER, Value, prctile) %>%
  rename(`%tile-instant` = prctile, `Latest Q` = Value) %>%
  left_join(pct_flow_last24 %>%
              st_set_geometry(NULL) %>%
              select(STATION_NUMBER, prctile) %>%
              rename(`%tile-last24` = prctile)) %>%
  left_join(pct_flow_7day_mean %>%
              st_set_geometry(NULL) %>%
              filter(Date == Sys.Date()) %>%
              select(STATION_NUMBER, prctile) %>%
              rename(`%tile-7day_mean` = prctile)) %>%
  left_join(num_year_data, by = c("STATION_NUMBER")) %>%
  arrange(STATION_NUMBER)


if(params$table_format == "latex"){
  pct_flow_instant_tbl_data %>%
    kable(format = "latex", booktabs = T, digits = 1) %>%
    kable_styling(font_size = 5,latex_options = c("HOLD_position"))
}

if(params$table_format == "html"){
  pct_flow_instant_tbl_data %>%
    kable(format = "html", digits = 2) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}
  
```


## Stations **much below normal**
If a location is not listed here there are no immediate low streamflow concerns. 
```{r}
much_below_normal_tbl <- pct_flow_instant %>%
  filter(pct_bin %in% c("Low","Much below normal (<10)")) %>%
  st_set_geometry(NULL) %>%
  select(STATION_NAME, STATION_NUMBER, Value, prctile) %>%
  rename(`Latest Q` = Value, `%tile` = prctile) %>%
  arrange(STATION_NUMBER)

if(params$table_format == "latex"){
  much_below_normal_tbl %>%
    kable(format = "latex", booktabs = T, digits = 2) %>%
    kable_styling(font_size = 7,latex_options = c("HOLD_position"))
}

if(params$table_format == "html"){
  much_below_normal_tbl %>%
    kable(format = "html", digits = 2) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

```

## Long-term Mean Annual Discharge (%MAD)

Flow needs during the  summer will range from juvenile rearing flows near 10-20 % (preferred) MAD to adult salmon/char passage flows  (>20%LT MAD) required prior to spawning.  Sub-standard flows (<10%LT MAD) can affect fish populations by reducing the area and quality of riffle habitats that generate fish food and aeration.  Flows nearing 5%LT MAD  are considered suboptimal for fish rearing and migration, indicate a degradation of instream habitat and may require  restrictions on water use. 

```{r mad}
## Calculate %MAD
long_term_mad <- hy_annual_stats(q_stns) %>%
  filter(Sum_stat == "MEAN") %>%
  spread(Sum_stat, Value) %>%
  group_by(STATION_NUMBER) %>%
  summarise(`MEAN MAD (m^3/s)` = mean(MEAN, na.rm = TRUE)) %>%
  left_join(rl_data_instant, by = c("STATION_NUMBER")) %>%
  mutate(`% MAD` = (Value/`MEAN MAD (m^3/s)`)*100) %>%
  left_join(allstations[,1:2], by = c("STATION_NUMBER")) %>%
  select(STATION_NAME, STATION_NUMBER, Value, `MEAN MAD (m^3/s)`, `% MAD`) %>%
  rename(`Latest Q` = Value) %>%
  arrange(STATION_NUMBER)

if(params$table_format == "latex"){
   long_term_mad %>%
    kable(format = "latex", booktabs = T, digits = 2) %>%
    kable_styling(font_size = 7,latex_options = c("HOLD_position"))
}

if(params$table_format == "html"){
   long_term_mad %>%
    kable(format = "html", digits = 2) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}
```




