---
output:
  pdf_document:
    pandoc_args: [
      "-V", "classoption=twocolumn"
    ]
    fig_caption: yes
  html_document:
    fig_caption: yes
geometry: margin=0.5in
params:
  table_format:
    value: latex
  prov:
    value: BC
  stns:
    value: 08MF005
  start_date: 
    value: !r as.Date("2015-01-01")
  end_date:
    value: !r as.POSIXct("2015-01-01 12:30:00")
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
library(hydrolook)
library(tidyhydat)
library(tidyverse)
library(lubridate)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "./")

## Create station header
stn_header <- allstations %>%
  filter(STATION_NUMBER == params$stns)
```

```{r results='asis'}
cat("#",stn_header$STATION_NAME,"-",stn_header$STATION_NUMBER, "\n")
```
## Hist

```{r}
HIST_FLOW <- DLY_FLOWS(STATION_NUMBER = params$stns)

HIST_FLOW %>%
  ggplot() +
  geom_histogram(aes(x = Value)) +
  #geom_vline(data = rl_data, aes(xintercept = Value, colour = Date)) +
  theme_minimal()
```

## Current
```{r}
rl_data = download_realtime_dd(STATION_NUMBER = params$stns)

rl_data_day <- rl_data %>%
  padr::thicken("day") %>%
  group_by(Date_day, STATION_NUMBER) %>%
  summarise(Value = mean(Value, na.rm = TRUE)) %>%
  filter(Date_day >= (Sys.Date()-30)) 

rl_data_day %>%
  ggplot(aes(x = Date_day, y = Value)) +
  geom_line() +
  geom_point()
```

## Hist

```{r}
HIST_FLOW <- DLY_FLOWS(STATION_NUMBER = params$stns)

HIST_FLOW %>%
  ggplot() +
  geom_histogram(aes(x = Value)) +
  #geom_vline(data = rl_data, aes(xintercept = Value, colour = Date)) +
  theme_minimal()
```

## Current
```{r}
rl_data = download_realtime_dd(STATION_NUMBER = params$stns)

rl_data_day <- rl_data %>%
  padr::thicken("day") %>%
  group_by(Date_day, STATION_NUMBER) %>%
  summarise(Value = mean(Value, na.rm = TRUE)) %>%
  filter(Date_day >= (Sys.Date()-30)) 

rl_data_day %>%
  ggplot(aes(x = Date_day, y = Value)) +
  geom_line() +
  geom_point()
```

## Some writing
ggplot() initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden. ggplot() initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden.ggplot() initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden.ggplot() initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden.ggplot() initializes a ggplot object. It can be used to declare the input data frame for a graphic and to specify the set of plot aesthetics intended to be common throughout all subsequent layers unless specifically overridden.
